---
title: My dynamic report
output: html_fragment
Author: Aiden Liu
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

```

## Analysing the ins and outs of peoples' daily walks
In this project, I am aiming to find insight on the key features during a person's daily walk. I utilised a google form attached to a google sheet to record my results into a table. Moreover, I exported my google sheets into a .csv file. I have 6 columns: Timestamp - The date and time in which the survey was completed, Time - Time the person took their daily walk, Weather - the type of weather during the person's daily walk, Crowdedness - how crowded the person's daily walk was, Joggers - whether the person saw people jogging or exercising during their walk, Pets - how many people did the person see walking their pets during the daily walk. 

- The following variables are categorical: Time, Weather, Crowdedness. 
- Joggers is a factor variable with 'yes' or 'no' as the input. 
- Pets is numeric.


```{r, echo=FALSE}
# Importing tidyverse
library(tidyverse)

# Reading in my survey data using the CSV url
csv_file = "https://docs.google.com/spreadsheets/d/e/2PACX-1vRJeCOOP8YYJj45QwShuwCptNM10PJCpOx8VQUR1dzOvwhcv9-4PX7cH2OedZYKVhsB5_mV3bvZvV1h/pub?output=csv"
logged_data = read_csv(csv_file)

# Renaming columns to one key word with respect to the columns
latest_data = rename(logged_data, Time = `What time do you usually have your daily walk?`, Weather = `What is the weather like when you are walking?`,
                     Crowdedness = `How crowded are your walks normally?`, Joggers = `Did you observe joggers or people exercising?`, 
                     Pets =`How many people did you see walking pets?`)

```

## Data Exploration with summary statistics

```{r, echo=FALSE}
# Calculating the minimum number of people seen walking their pets
min.pets = min(latest_data$Pets)
min.pets.comment = paste("The smallest number of pets seen on a daily walk is", min.pets)
print(min.pets.comment)
```
```{r,echo=FALSE}
# Calculating the maximum number of people seen walking their pets
max.pets = max(latest_data$Pets)
max.pets.comment = paste("The largest number of pets seen on a daily walk is", max.pets)
print(max.pets.comment) 
```

```{r, echo=FALSE}
# How many people saw joggers or people exercising on their walk?
no.of.joggers = latest_data %>% 
  filter(Joggers == "Yes") %>% # Keeping rows with only Yes in the Joggers column
  summarise(count = n()) %>% # Keeping the size of the number of rows
  pull(count)
joggers.comment = paste("Around", no.of.joggers, "People saw joggers on their daily walk")
print(joggers.comment)
```

```{r, echo=FALSE}
# What was the most common crowdedness during peoples daily walks?
mode.crowdedness = latest_data %>%
  count(Crowdedness, sort = TRUE) %>%
  slice(1) %>% 
  select(-n)
most.crowdedness.comment = paste("The most common crowdedness during peoples' daily walk is:", mode.crowdedness)
print(most.crowdedness.comment)
```

```{r, echo=FALSE}
# What was the least common crowdedness during peoples daily walks?
least.crowdedness = latest_data %>%
  count(Crowdedness, sort = TRUE) %>% 
  slice(4) %>% 
  select(-n)
least.crowdedness.comment = paste("The least common crowdedness during peoples' daily walk is:", least.crowdedness)
print(least.crowdedness.comment) 
```

```{r, echo=FALSE}
# What is the most common times people have their daily walks?
mode.time = latest_data %>%
  count(Time, sort = TRUE) %>%
  slice(1) %>% 
  select(-n)
mode.time.comment = paste("The most common time people have their daily walk is:", mode.time)
print(mode.time.comment)
```

## Bar Chart of the times people have their daily walks vs count
```{r, echo=FALSE}
# Creating a bar chart of the times people have their daily walks vs count
ggplot(data = latest_data, mapping = aes(x=Time))+
  geom_bar(fill = "orange") + # Making the bar chart orange
  labs(title = "Bar Chart of the times people have their daily walks", x = "Time of day", y = "Count")+ # Labeling my bar chart
  theme(plot.title = element_text(hjust = 0.5))+ # Centering my title
  scale_y_continuous(labels = scales::number_format(accuracy = 1)) # Keeping only whole numbers on the y-axis
```

## Bar Chart of the types of crowdedness during peoples' daily walks
```{r,echo=FALSE}
# Creating a bar chart of the types of crowdedness during peoples' daily walks
ggplot(data = latest_data, mapping=aes(x=Crowdedness))+
  geom_bar(fill="lightblue") + # Making the bar light blue
  labs(title="Bar Chart of the Crowdedness people experience on their daily walks", x="Crowdedness", y="Count")+ # Labeling my bar chart
  theme(plot.title = element_text(hjust = 0.5))+ # Centering my title
  scale_x_discrete(expand = expansion(mult = 0.05)) # Adding spacing between names of variables on x-axis to avoid names overlapping
```